\bf What is the Best Way to Display Two Time Series to Read Association?

### 2016-02-09 paper/paper.Rnw
editing section 4

Where $T_{x}$ is all possible sets of $x$ trials out of $K$ resulting in a success, $A \in T_{x}$ is a specific set of $x$ trials resulting in a success and $A^{c}$ is the complement to $A$, the set of $K-x$ trials resulting in a failure.

@@

Further analysis was carried out using \citet{R} version 3.1.2 and \citet{Rstudio} version 0.99.484 using the packages: dplyr, ggplot2, grid, gridExtra, gridSVG, knitr, maps, mFilter, mnormt, nullabor, stringr and tidyr.
%\citet{dplyr}, \citet{ggplot2}, \citet{grid}, \citet{gridExtra}, \citet{gridSVG}, \citet{knitr}, \citet{maps}, \citet{mFilter}, \citet{mnormt}, \citet{nullabor}, \citet{stringr} and \citet{tidyr}.

>>>>

Where $T_{x}$ is all possible sets of $x$ trials out of $K$ resulting in a success, $A \in T_{x}$ is a specific set of $x$ trials resulting in a success and $A^{c}$ is the complement to $A$, the set of $K-x$ trials resulting in a failure. This can easily be calculated using the poibin package for R.

@@

Further analysis was carried out using \citet{R} version 3.1.2 and \citet{Rstudio} version 0.99.484 using the packages: dplyr, ggplot2, grid, gridExtra, gridSVG, knitr, maps, mFilter, mnormt, nullabor, poibin, stringr and tidyr.
%\citet{dplyr}, \citet{ggplot2}, \citet{grid}, \citet{gridExtra}, \citet{gridSVG}, \citet{knitr}, \citet{maps}, \citet{mFilter}, \citet{mnormt}, \citet{nullabor}, \citet{poibin}, \citet{stringr} and \citet{tidyr}.
